Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2018-01-04 ms.tex
amplitudes/offsets

\subsection{Hotspot Offset}
The location of peak brightness of the phase curve is a proxy for the efficiency of thermal reradiation to space and relative to heat transport by advection (the radiative-to-advective timescale). The faster the reradiation, the less heat can be redistributed to the nightside. We compared the measured hotspot offset for the different models and found FIXME.

>>>>

\subsection{Phase Curve Amplitude and Hotspot Offset}
The location of peak brightness of the phase curve is a proxy for the efficiency of thermal reradiation to space and relative to heat transport by advection (the radiative-to-advective timescale). The faster the reradiation, the less heat can be redistributed to the nightside. We compared the measured hotspot offset for the different models and found FIXME.
